\pkg{RProtoBuf}: Efficient Cross-Language Data Serialization in \proglang{R}

### 2014-01-26 papers/jss/article.Rnw
make the directory structure a little more organized
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/rprotobuf@850 edb9625f-4e0d-4859-8d74-9fd3b1da38cb
section and subsection in sentence style
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/rprotobuf@851 edb9625f-4e0d-4859-8d74-9fd3b1da38cb

\begin{document}
\SweaveOpts{concordance=FALSE}

@@

% Lets place this at the top of the page or the bottom, or on a float
% page, but not just here in the middle of the page.
\begin{figure}[tbp]
\begin{center}
\includegraphics[width=\textwidth]{protobuf-distributed-system-crop.pdf}
\end{center}
\caption{Example protobuf usage}
\label{fig:protobuf-distributed-usecase}
\end{figure}

@@

\section{Basic Usage: Messages and Descriptors}
\label{sec:rprotobuf-basic}

@@

\subsection[Importing Message Descriptors from .proto files]{Importing Message Descriptors from \texttt{.proto} files}

@@

\section{Under the hood: S4 Classes, Methods, and Pseudo Methods}
\label{sec:rprotobuf-classes}

@@

\subsection{Field Descriptors}
\label{subsec-field-descriptor}

@@

\subsection{Enum Descriptors}
\label{subsec-enum-descriptor}

@@

\subsection{File Descriptors}
\label{subsec-file-descriptor}

@@

\subsection{Enum Value Descriptors}
\label{subsec-enumvalue-descriptor}

@@

\section{Type Coercion}
\label{sec:types}

@@

\subsection{Unsigned Integers}

@@

\section[Converting R Data Structures into Protocol Buffers]{Converting \proglang{R} Data Structures into Protocol Buffers}
\label{sec:evaluation}

@@

\subsection[Evaluation: Converting R Data Sets]{Evaluation: Converting \proglang{R} Data Sets}

@@

\subsection{Compression Performance}
\label{sec:compression}

@@

\section{Application: Distributed Data Collection with MapReduce}
\label{sec:mapreduce}

@@

\begin{figure}[h!]
\begin{center}
\includegraphics[width=\textwidth]{histogram-mapreduce-diag1.pdf}
\end{center}
\caption{Diagram of MapReduce Histogram Generation Pattern}
\label{fig:mr-histogram-pattern1}
\end{figure}

@@

\section{Application: Data Interchange in Web Services}
\label{sec:opencpu}

>>>>

\begin{document}
\SweaveOpts{concordance=FALSE,prefix.string=figures/fig}

@@

% Lets place this at the top of the page or the bottom, or on a float
% page, but not just here in the middle of the page.
\begin{figure}[tbp]
\begin{center}
\includegraphics[width=\textwidth]{figures/protobuf-distributed-system-crop.pdf}
\end{center}
\caption{Example protobuf usage}
\label{fig:protobuf-distributed-usecase}
\end{figure}

@@

\section{Basic Usage: Messages and descriptors}
\label{sec:rprotobuf-basic}

@@

\subsection[Importing message descriptors from .proto files]{Importing message descriptors from \texttt{.proto} files}

@@

\section{Under the hood: S4 classes, methods, and pseudo methods}
\label{sec:rprotobuf-classes}

@@

\subsection{Field descriptors}
\label{subsec-field-descriptor}

@@

\subsection{Enum descriptors}
\label{subsec-enum-descriptor}

@@

\subsection{File descriptors}
\label{subsec-file-descriptor}

@@

\subsection{Enum value descriptors}
\label{subsec-enumvalue-descriptor}

@@

\section{Type coercion}
\label{sec:types}

@@

\subsection{Unsigned integers}

@@

\section[Converting R data structures into Protocol Buffers]{Converting \proglang{R} data structures into Protocol Buffers}
\label{sec:evaluation}

@@

\subsection[Evaluation: Converting R data sets]{Evaluation: Converting \proglang{R} data sets}

@@

\subsection{Compression performance}
\label{sec:compression}

@@

\section{Application: Distributed data collection with MapReduce}
\label{sec:mapreduce}

@@

\begin{figure}[h!]
\begin{center}
\includegraphics[width=\textwidth]{figures/histogram-mapreduce-diag1.pdf}
\end{center}
\caption{Diagram of MapReduce Histogram Generation Pattern}
\label{fig:mr-histogram-pattern1}
\end{figure}

@@

\section{Application: Data Interchange in web Services}
\label{sec:opencpu}
